\mytitle

### 2023-06-02 chapters/depsynth/related.tex
x

\paragraph{Program synthesis for systems code.}
Transit~\cite{udupa:transit} is a tool for automatically inferring distributed protocols
such as those used for cache coherence.
It guides the search using \emph{concolic} snippets~\cite{sen:concolic}---%
effectively litmus tests that can be partially symbolic---%
and finds a protocol that satisfies those snippets for \emph{any} ordering of messages.
MemSynth~\cite{bornholt:memsynth} is a program synthesis tool for
automatically constructing specifications of memory consistency models.
MemSynth takes similar inputs to \depsynth---a set of litmus tests and a target language---%
and its synthesizer generates and checks happens-before graphs for those tests.
Adopting MemSynth's aggressive inference of partial interpretations~\cite{torlak:kodkod}
to shrink the search space of happens-before graphs would be promising future work.

>>>>

\paragraph{Program synthesis for systems code.}
Transit~\cite{udupa:transit} is a tool for automatically inferring distributed protocols
such as those used for cache coherence.
It guides the search using \emph{concolic} snippets~\cite{sen:concolic}---%
effectively litmus tests that can be partially symbolic---%
and finds a protocol that satisfies those snippets for \emph{any} ordering of messages.
MemSynth~\cite{bornholt:memsynth} is a program synthesis tool for
automatically constructing specifications of memory consistency models.
MemSynth takes similar inputs to \depsynth---a set of litmus tests and a target language---%
and its synthesizer generates and checks happens-before graphs for those tests.
Adopting MemSynth's aggressive inference of partial interpretations~\cite{torlak:kodkod}
to shrink the search space of happens-before graphs would be promising future work.\tighten
\vspace*{-1em}

### 2023-06-02 thesis.tex
x

  Reading Commitee: \\
  Emina Torlak, Chair \\
  Xi Wang \\
  Zachary Tatlock \\
  Shane Steinert-Threlkeld
  \vfill

@@

% Emina
Over the past five years, I've had the priviledge of working with
of Emina Torlak. She is everything I could have possibly asked for
in a mentor. From getting into the Rosette weeds to career chats over Molly Moon's,
she always seems to know exactly what I need to hear and when I need to hear it.
Thanks for always believing me and keeping me moving forward.

>>>>

  Reading Commitee: \\
  Emina Torlak, Chair \\
  Xi Wang \\
  Zachary Tatlock %\\
  %Shane Steinert-Threlkeld
  \vfill

@@

% Emina
Over the past five years, I've had the privilege of working with
of Emina Torlak. She is everything I could have possibly asked for
in a mentor. From getting into the Rosette weeds to career chats over Molly Moon's,
she always seems to know exactly what I need to hear and when I need to hear it.
Thanks for always believing me and keeping me moving forward.
